Dynamics of isoflurane-induced vasodilation and blood flow of cerebral vasculature revealed by multi-exposure speckle imaging

### 2021-10-27 article.tex
Response to Reviewer #2 (Partial)

\subsection{Multi-Exposure Speckle Imaging (MESI)}
A schematic of the imaging system is presented in Fig.~\ref{fig:system}a. MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle. The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) with $2\times$ magnification and cropped to a field-of-view of 3.6 $\times$ 3.0 mm. Camera exposures were temporally synchronized with the modulated laser pulses. Fifteen camera exposures ranging between 50 $\mu$s and 80 ms \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second. The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages \cite{Sullender:2018ff}.

@@

The correction for multiple dynamic scattering events applied to the vascular MESI measurements cannot be directly translated to the parenchyma regions \cite{Kazmi:2015du}. Therefore all parenchyma MESI measurements assume only a single dynamic scattering event per photon, which is not a reliable representation of the underlying dynamics \cite{Davis:2015ij}. Recent efforts to directly measure the intensity autocorrelation function have produced a modified speckle contrast model that assumes both multiple scattering and unordered dynamics \cite{Postnov.2020}. Applying this correction could improve the robustness of the MESI measurements in parenchyma regions, particularly when there are significant reductions in flow.

>>>>

\subsection{Multi-Exposure Speckle Imaging (MESI)}
A schematic of the imaging system is presented in Fig.~\ref{fig:system}a. MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle. The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) with $2\times$ magnification and cropped to a field-of-view of 3.6 $\times$ 3.0 mm. Camera exposures were temporally synchronized with the modulated laser pulses. Fifteen camera exposures spanning three orders of magnitude (0.05, 0.075, 0.1, 0.25, 0.5, 0.75, 1.0, 2.5, 5.0, 7.5, 10, 25, 40, 50, and 80 ms) \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second. The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages \cite{Sullender:2018ff}.

@@

The correction for multiple dynamic scattering events applied to the vascular MESI measurements cannot be directly translated to the parenchyma regions \cite{Kazmi:2015du}. Therefore all parenchyma MESI measurements assume only a single dynamic scattering event per photon, which is not a reliable representation of the underlying dynamics \cite{Davis:2015ij}. Recent efforts to directly measure the intensity autocorrelation function have produced a modified speckle contrast model that assumes both multiple scattering and unordered dynamics \cite{Postnov.2020}. Applying this correction could improve the robustness of the MESI measurements in parenchyma regions, particularly when there are major changes in flow.
